---
title: "Capstone Project Diabetes Dataset"
author: "Dani Herzberg"
date: "10/27/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)


library(plyr)
library(tidyverse)
library(readxl)
library(moments) # assess skewness
library(gdata)
library(stringr)
library(lubridate)
library(scales)
library(graphics)
library(caret)
library(magrittr)
library(tidyr)
library(reshape2)
library(plotly)
library(car) # run qq plot
library(lmtest) # assess homoscedasticity
library(MASS)
library(faraway)
library(e1071)
library(dplyr)
library(ggplot2)
library(class)
library(caret)
library(data.table)
library(ROCR)
library(ROSE) #Sampling-over and under, ROC and AUC curve
library(tidyverse)
library("rdd")
library(Formula)
library("rddensity")
library("gridExtra")
library(ivreg)
library(dataprep)
library("Synth")
library(jtools)
library(kableExtra)
library("funModeling") 
library(tidyverse) 
library(Hmisc)
library("corrplot")
library("mice")
library("ggcorrplot")
library("janitor")
library("vtree")


```

## Load Packages

```{r data}
getwd()
diabetes.data <- read.csv("diabetic_data.csv")
# diabetes.data <- read.csv("Desktop/Georgetown/Hoya 7/diabetic_data.csv")
head(diabetes.data)
str(diabetes.data)
dim(diabetes.data)
```
## Introduction to Bias


## Preliminary EDA

The data set is comprised of 101766 observations of 50 columns. This means that there are just over 500k data points. 
There were also some missing variables in this data - but this was mainly seen in columns that do not appear to be crucial to our analysis

```{r load data}

#preliminary EDA
glimpse(diabetes.data)

#convert the following to numeric: diabetesMed, readmitted, change, insulin, gender, race, age, weight, medical_specialty 
# can add more later - but this is used for start of analysis 
# how to pick which out of the 50 columns are important for analysis?? 
diabetes.data$diabetesMed = as.numeric(diabetes.data$diabetesMed)
diabetes.data$readmitted = as.factor(diabetes.data$readmitted)
diabetes.data$change = as.factor(diabetes.data$change)
diabetes.data$insulin = as.factor(diabetes.data$insulin)
diabetes.data$gender = as.factor(diabetes.data$gender)
diabetes.data$race = as.factor(diabetes.data$race)
diabetes.data$age = as.factor(diabetes.data$age)
# diabetes.data$weight = as.numeric(diabetes.data$weight)
diabetes.data$medical_specialty = as.factor(diabetes.data$medical_specialty)

#checking missing values
diabetes.data  %>%
  summarise_all(list(~is.na(.)))%>%
  pivot_longer(everything(),
               names_to = "variables", values_to="missing") %>%
  count(variables, missing) %>%
  ggplot(aes(y=variables,x=n,fill=missing))+
  geom_col()

#re-check missing values 
sum(is.na(diabetes.data)) # this is only with the variables that were included above, I think issue with ? in file 

#Data Distribution
freq(diabetes.data) 
freq(diabetes.data$readmitted) 


#Data Profiling
print(profiling_num(diabetes.data))
plot_num(diabetes.data)

```

## Data Distribution 

```{r data dist}

tabyl(diabetes.data, readmitted, number_diagnoses) # can pick something else for number_diagnoses 

tabyl(diabetes.data, readmitted, number_diagnoses) %>%
  adorn_percentages("col") %>%
  adorn_pct_formatting(digits = 1)


vtree(diabetes.data, c("readmitted", "gender"), 
  horiz = FALSE, fillcolor = c(LanguageGroup = "#e7d4e8", 
  Gender = "#99d8c9", Hobbyist = "#9ecae1"), 
  keep = list(LanguageGroup = c("R", "Both")), showcount = FALSE) 

vtree(diabetes.data, c("readmitted", "race"), 
  horiz = FALSE, fillcolor = c(LanguageGroup = "#e7d4e8", 
  Gender = "#99d8c9", Hobbyist = "#9ecae1"), 
  keep = list(LanguageGroup = c("R", "Both")), showcount = FALSE) 

vtree(diabetes.data, c("readmitted", "insulin"), 
  horiz = FALSE, fillcolor = c(LanguageGroup = "#e7d4e8", 
  Gender = "#99d8c9", Hobbyist = "#9ecae1"), 
  keep = list(LanguageGroup = c("R", "Both")), showcount = FALSE) 

```


## Data Cleanup 
# Next Steps: pick top vars, unless we want a corr plot with 50 vars
Vars that we want to use listed below (can update, if needed)
race, gender, age, Admission type, Discharge disposition
Admission source, Time in hospital, 
Payer code (52% missing - but this could also be biased bc it involves insurance)
Number of lab procedures, Number of procedures, Number of medications,
Number of outpatient visits, Number of emergency visits, Number of inpatient visits
Number of diagnoses, Change of medications, Diabetes medications

```{r data clean}
head(diabetes.data)
head(diabetes.data1)
diabetes.data1 = diabetes.data[-1] # removing encounter id
names(diabetes.data1)

#Female is 1 and Male is 2
diabetes.data1$gender = as.factor(diabetes.data1$gender)
diabetes.data1$gender = as.numeric(diabetes.data1$gender)

#Every readmitted Yes = 1 and No = 0 
head(diabetes.data1$readmitted)
diabetes.data1$readmitted<-ifelse(diabetes.data1$readmitted=="NO",0,1)
diabetes.data1$readmitted = as.numeric(diabetes.data1$readmitted)

# removing extra columns before more var clean up 
diabetes.data2 = diabetes.data1[, c("race", "gender", "age", "admission_type_id", 
          "discharge_disposition_id", "admission_source_id", "time_in_hospital",
          "num_lab_procedures", "num_procedures","num_medications", "number_outpatient",
          "number_emergency", "number_inpatient", "number_diagnoses","change",
          "readmitted" )]
head(diabetes.data2)
str(diabetes.data2)

#age buckets into int
diabetes.data2$age = as.integer(diabetes.data1$age)

# change in meds - change is 1, no change is 0
diabetes.data2$change = ifelse(diabetes.data2$change=="NO",0,1)
diabetes.data2$change = as.numeric(diabetes.data1$change)

# race into num
diabetes.data2$race = as.factor(diabetes.data1$race)
diabetes.data2$race = as.numeric(diabetes.data1$race)

```


## Impute for Missing Values

```{r load data}
sum(is.na(diabetes.data2)) #there appears to be no missing values in the columns selected for use
summary(diabetes.data2)
#Here we will use the mice package that will help us do the imputation (we are going for 1 imputation, m=1)

#impute_stroke <-mice(stroke.data,m=1,seed = 1111)
#stroke.data<-complete(impute_stroke,1)
#str(stroke.data)

#impute_stroke <-mice(stroke.data1,m=1,seed = 1111)
#stroke.data1<-complete(impute_stroke,1)
#str(stroke.data1)

```

## Incremental Analytics 

```{r load data}

#Correlation Analysis
str(diabetes.data2)
correlation = cor(diabetes.data2)

corrplot(cor(diabetes.data2), method = "shade", tl.col = "black", tl.cex = .75) 

corrplot(cor(diabetes.data2), type = "lower", tl.col = "black", tl.cex = .9) 

```

No correlations seen to start - but could bias here be causing some correlations to be unseen? 

```{r split}
# 1. Data Partition
set.seed(123)
index <- sample(1:nrow(diabetes.data2), round(nrow(diabetes.data2) * 0.7))
train <- diabetes.data2[index, ] 
test <- diabetes.data2[-index, ]
length(train$readmitted) # 71236
length(test$readmitted) # 30530

table(train$readmitted) 
table(test$readmitted) 
prop.table(table(train$readmitted))
prop.table(table(test$readmitted))

# confirm no data is missing 
colSums(is.na(train))
colSums(is.na(test))

```


```{r echo = FALSE}
myLogitAll <- glm(readmitted  ~ . , data = test, family = "binomial")
summary(myLogitAll)
vif(myLogitAll)


```


```{r echo = FALSE}
# roc
readmitt_pred <- predict(object = myLogitAll, newdata = test, type = "response")
roc_pred <- prediction(predictions = readmitt_pred , labels = test$readmitted)
roc_perf <- performance(roc_pred , "tpr" , "fpr") 
plot(roc_perf,
colorize = TRUE, print.cutoffs.at= seq(0,1,0.05), text.adj=c(-0.2,1.7))

as.numeric(performance(roc_pred, "auc")@y.values)

importance = varImp(myLogitAll)
print(importance)
```


```{r echo = FALSE}



```


```{r echo = FALSE}



```