---
title: "Capstone Project Diabetes Dataset"
author: "Dani Herzberg"
date: "10/27/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)


library(plyr)
library(tidyverse)
library(readxl)
library(moments) # assess skewness
library(gdata)
library(stringr)
library(lubridate)
library(scales)
library(graphics)
library(caret)
library(magrittr)
library(tidyr)
library(reshape2)
library(plotly)
library(car) # run qq plot
library(lmtest) # assess homoscedasticity
library(MASS)
library(faraway)
library(e1071)
library(dplyr)
library(ggplot2)
library(class)
library(caret)
library(data.table)
library(ROCR)
library(ROSE) #Sampling-over and under, ROC and AUC curve
library(tidyverse)
library("rdd")
library(Formula)
library("rddensity")
library("gridExtra")
library(ivreg)
library(dataprep)
library("Synth")
library(jtools)
library(kableExtra)
library("funModeling") 
library(tidyverse) 
library(Hmisc)
library("corrplot")
library("mice")
library("ggcorrplot")
library("janitor")
library("vtree")


```

## Load Packages

```{r data}
getwd()
diabetes.data <- read.csv("diabetic_data.csv")
# diabetes.data <- read.csv("Desktop/Georgetown/Hoya 7/diabetic_data.csv")
head(diabetes.data)
str(diabetes.data)
dim(diabetes.data)
```
## Introduction to Bias


## Preliminary EDA

The data set is comprised of 101766 observations of 50 columns. This means that there are just over 500k data points. 
There were also some missing variables in this data - but this was mainly seen in columns that do not appear to be crucial to our analysis

```{r load data}

#preliminary EDA
glimpse(diabetes.data)

#convert the following to numeric: diabetesMed, readmitted, change, insulin, gender, race, age, weight, medical_specialty 
# can add more later - but this is used for start of analysis 
# how to pick which out of the 50 columns are important for analysis?? 
diabetes.data$diabetesMed = as.numeric(diabetes.data$diabetesMed)
diabetes.data$readmitted = as.factor(diabetes.data$readmitted)
diabetes.data$change = as.factor(diabetes.data$change)
diabetes.data$insulin = as.factor(diabetes.data$insulin)
diabetes.data$gender = as.factor(diabetes.data$gender)
diabetes.data$race = as.factor(diabetes.data$race)
diabetes.data$age = as.factor(diabetes.data$age)
# diabetes.data$weight = as.numeric(diabetes.data$weight)
diabetes.data$medical_specialty = as.factor(diabetes.data$medical_specialty)

#checking missing values
diabetes.data  %>%
  summarise_all(list(~is.na(.)))%>%
  pivot_longer(everything(),
               names_to = "variables", values_to="missing") %>%
  count(variables, missing) %>%
  ggplot(aes(y=variables,x=n,fill=missing))+
  geom_col()

#re-check missing values 
sum(is.na(diabetes.data)) # this is only with the variables that were included above, I think issue with ? in file 

#Data Distribution
freq(diabetes.data) 
freq(diabetes.data$readmitted) 


#Data Profiling
print(profiling_num(diabetes.data))
plot_num(diabetes.data)

```

## Data Distribution 

```{r data dist}

tabyl(diabetes.data, readmitted, number_diagnoses) # can pick something else for number_diagnoses 

tabyl(diabetes.data, readmitted, number_diagnoses) %>%
  adorn_percentages("col") %>%
  adorn_pct_formatting(digits = 1)


vtree(diabetes.data, c("readmitted", "gender"), 
  horiz = FALSE, fillcolor = c(LanguageGroup = "#e7d4e8", 
  Gender = "#99d8c9", Hobbyist = "#9ecae1"), 
  keep = list(LanguageGroup = c("R", "Both")), showcount = FALSE) 

vtree(diabetes.data, c("readmitted", "race"), 
  horiz = FALSE, fillcolor = c(LanguageGroup = "#e7d4e8", 
  Gender = "#99d8c9", Hobbyist = "#9ecae1"), 
  keep = list(LanguageGroup = c("R", "Both")), showcount = FALSE) 

vtree(diabetes.data, c("readmitted", "insulin"), 
  horiz = FALSE, fillcolor = c(LanguageGroup = "#e7d4e8", 
  Gender = "#99d8c9", Hobbyist = "#9ecae1"), 
  keep = list(LanguageGroup = c("R", "Both")), showcount = FALSE) 

```


## Data Cleanup -- ENDED HERE Oct 29
# Next Steps: pick top vars, unless we want a corr plot with 50 vars 

```{r load data}

stroke.data1 = stroke.data[-1]

#Female is 1 and Male is 2
stroke.data1$gender = as.factor(stroke.data1$gender)
stroke.data1$gender = as.numeric(stroke.data1$gender)

#Every Married Yes = 1 and No = 0 
stroke.data1$ever_married<-ifelse(stroke.data1$ever_married=="Yes",1,0)
stroke.data1$ever_married = as.numeric(stroke.data1$ever_married)


stroke.data1$work_type = as.factor(stroke.data1$work_type)
stroke.data1$work_type = as.numeric(stroke.data1$work_type)

stroke.data1$Residence_type = as.factor(stroke.data1$Residence_type)
stroke.data1$Residence_type = as.numeric(stroke.data1$Residence_type)

stroke.data1$smoking_status = as.factor(stroke.data1$smoking_status)
stroke.data1$smoking_status = as.numeric(stroke.data1$smoking_status)


str(stroke.data1)

```


## Impute for Missing Values

```{r load data}

#Here we will use the mice package that will help us do the imputation (we are going for 1 imputation, m=1)

impute_stroke <-mice(stroke.data,m=1,seed = 1111)
stroke.data<-complete(impute_stroke,1)
str(stroke.data)

impute_stroke <-mice(stroke.data1,m=1,seed = 1111)
stroke.data1<-complete(impute_stroke,1)
str(stroke.data1)

```

## Incremental Analytics 

```{r load data}

#Correlation Analysis

correlation = cor(stroke.data1)

corrplot(cor(stroke.data1), method = "shade", tl.col = "black", tl.cex = .75) 

corrplot(cor(stroke.data1), type = "lower", tl.col = "black", tl.cex = .9) 

```



```{r echo = FALSE}



```